Comparisons in three center

### 2020-12-17 scripts/40_combine_all_samp_pheno.Rmd
was very stimulated and ..

# save one for my own
all %>% 
  write_csv('../data/shotgun_pheno/final_comprehensive.csv')
```

@@

>>>>

# save one for my own
all %>% 
  write_csv('../data/shotgun_pheno/final_comprehensive.csv')

all <- read_csv('../data/shotgun_pheno/final_comprehensive.csv')
```

@@

```{r}
tally <- ALL %>% 
  select(center, outcome) %>% 
  mutate_if(is.factor, as.character) %>% 
  gather('metric', 'value', cr_d100 : crs) %>% 
  count(center, metric, value) %>% 
  filter(value != 'not_assessed') %>% 
  spread('metric', 'n', fill = 0)
```

```{r}
library(kableExtra)

kbl(tally, caption = "") %>%
  kable_classic_2( full_width = F) %>%
  pack_rows("Group Italy", 1, 2) %>%
  pack_rows("Group MSK", 3, 4) %>% 
  pack_rows("Group UPENN", 5, 6)

```

### 2020-12-17 scripts/43_comparisons_3.Rmd
udpate
was very stimulated and ..

```{r}
# a tally of the table
all <- read_csv('../data/shotgun_pheno/final_simplified.csv')

all %>% 
  split(.$center) %>% 
  map_dfr(~ count(x = ., cr_d100), .id = 'center')

all %>% 
  count(toxicity)

```

```{r}
pheno <- read_csv('../data/shotgun_pheno/final_simplified.csv') %>% 
  gather('pheno', 'value', cr_d100:toxicity)

@@

all_pcts <- all_sub_pheno %>% 
  map(~ pull(.data = ., fid) ) %>% 
  imap(~ full %>% select(`# Pathway`, matches(.x)) %>% 
         write_tsv(str_glue('../data/shotgun_output/humann3/pull_{.y}_pcts.tsv')))

all_gfcts <- all_sub_pheno %>% 
  map(~ pull(.data = ., fid) ) %>% 
  imap(~ fullgenefam %>% select(`# Gene Family`, matches(.x)) %>% 
         write_tsv(str_glue('../data/shotgun_output/humann3/pull_{.y}_gfcts.tsv'))) 
```

@@

```{r}
fns <- list.files('../data/shotgun_output/humann3/', pattern = 'lefse_ready')

@@

>>>>

```{r}
pheno <- read_csv('../data/shotgun_pheno/final_comprehensive.csv') %>% 
  select(fid, center, cr_d100, toxicity, icans, crs) %>% 
  gather('pheno', 'value', cr_d100:crs)

@@

all_pcts <- all_sub_pheno %>% 
  map(~ pull(.data = ., fid) ) %>% 
  imap(~ full %>% select(`# Pathway`, matches(.x)) %>% 
         write_tsv(str_glue('../data/shotgun_output/humann3/pull_{.y}_pcts.tsv')))
```

```{r}
all_gfcts <- all_sub_pheno %>% 
  map(~ pull(.data = ., fid) ) %>% 
  imap(~ fullgenefam %>% select(`# Gene Family`, matches(.x)) %>% 
         write_tsv(str_glue('../data/shotgun_output/humann3/pull_{.y}_gfcts.tsv'))) 
```

@@

```{r}
fns <- list.files('../data/shotgun_output/humann3/', pattern = 'lefse_ready_pcts.tsv$')

@@

## The taxa relative abundance from the shotgun data using metaphlan

```{r}
taxa <- read_tsv('../data/shotgun_output/metaphlan/merged_abundance_table.txt', skip = 1)  %>% 
  rename_all(funs(str_replace(., '_profile$','')))

tcts <- sub_phenos %>% 
  map(~ pull(.data = ., fid) ) %>% 
  imap(~ taxa %>% select(clade_name, matches(.x)) %>% 
         write_tsv(str_glue('../data/shotgun_output/humann3/{.y}_tcts.tsv')))

all_tcts <- all_sub_pheno %>% 
  map(~ pull(.data = ., fid) ) %>% 
  imap(~ taxa %>% select(clade_name, matches(.x)) %>% 
         write_tsv(str_glue('../data/shotgun_output/humann3/pull_{.y}_tcts.tsv')))
```

```{r}
# run lefse
fns <- list.files('../data/shotgun_output/humann3/', pattern = 'lefse_ready_tcts.tsv$')

cmds <- tibble(
  fns = fns
) %>% 
  mutate(format_cmd = str_glue('format_input.py {fns}  {fns}.in -c 1 -u 2 -o 1000000')) %>% 
  mutate(run_cmd = str_glue('run_lefse.py {fns}.in  {fns}.res')) %>% 
  mutate(plot_cmd = str_glue('plot_res.py {fns}.res {fns}.png  --feature_font_size 4 --width 10 --dpi 300')) %>% 
  mutate(clado_cmd = str_glue('plot_cladogram.py {fns}.res {fns}_clado.png  --label_font_size 4 --dpi 300 --format png --title {fns}')) %>% 
  select(-fns) %>% 
  gather() %>% 
  select(value) %>% 
  write_csv('../data/shotgun_output/humann3/lefse_run_cmd_taxa.sh', col_names = F)
```
